---
title: Reversible R Markdown Document
subtitle: Your subtitle
author: Your Name
date: Created `r Sys.Date()`
output:
  redoc::redoc:
    highlight_outputs: yes
    margins: 1
    line_numbers: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is an example Reversible R Markdown document. It will preserve code
elements for restoration in your final `.docx` file.

You can use things like inline <!--- an HTML comment ---> comments.

You can use code chunks to generate output and they will be restored:

```{r cars}
summary(cars)
```

Inline text
-----------

```{r, echo = FALSE, results = 'hide'}
# A non-included chunk to provide inline chunks with values.
a <- 2
b <- 3
```

You can include calculations inline like so: `r a` plus
`r b` equals `r a + b`. Even empty inline
chunks `r NULL` will be stored and marked with hidden text in
the Word document.

Chunks with plots
-----------------

You can of course also embed plots, for example:

```{r pressure, dev.args=list(bg='transparent')}
plot(pressure)
```

Track Changes
-------------

**redoc** supports [Critic Markup](http://criticmarkup.com/users-guide.php)
syntax for comments. You can include edits and they will be converted to tracked
changes in your {==  Word document  ==}{>> Neat! <<}. By default , your system
username is used as the author of changes, but this can be set with the
`comment_author` argument in `redoc()` or your document YAML.

{==  So if I add some changes here, what does it do? where does it go? Does it
create a new word file? Does it overwrite the old? Lets test it out and see what
happens.  ==}{>> Testing a tracked change in Rmarkdown <<}

So what happens when I make changes in word?
